diffusion, websites with 1 pc

### 2023-03-20 src/hex_heatmaps.Rmd
lisa per firm

    stat_binhex(bins=150) + 
    geom_polygon(data = gb.df, aes(x=long, y = lat, group = group), #gb.df
                 fill=NA, color = "black", size = 0.1, alpha = 0.8)+
    scale_fill_gradientn(colours=c('light gray','blue'),
                         name='Frequency',na.value=NA) + #, trans = "log10") +
    coord_equal() +
    labs(x=NULL, y=NULL) +
    geom_point(data = cities, aes(x=long, y=lat), colour = "black", size = .1) + 
    geom_text(size = 2, check_overlap = F, nudge_y = .2, data = cities, aes(x=long, y=lat, label = name)) +
    #theme(legend.key.size = unit(0.05, "cm")) + # legend.key.width=unit(1, "cm"), 
    ggmap::theme_nothing(legend = T) +
    theme(legend.title=element_text(size=5.5), legend.text=element_text(size=4)) +
    #theme(legend.position=c(0.075,0.28))
    guides(fill = guide_colorbar(barwidth = 0.5, barheight = 2.5)) +
    ggtitle(t)
  ggsave(p, filename = paste(path.out, t, ".png", sep = ""))
}
```
## hex heatmaps log transformed

>>>>

    stat_binhex(bins=150) + 
    geom_polygon(data = gb.df, aes(x=long, y = lat, group = group), #gb.df
                 fill=NA, color = "black", size = 0.1, alpha = 0.8)+
    scale_fill_gradientn(colours=c('light gray','blue'),
                         name='Frequency',na.value=NA) + #, trans = "log10") +
    coord_equal() +
    labs(x=NULL, y=NULL) +
    geom_point(data = cities, aes(x=long, y=lat), colour = "black", size = .1) + 
    geom_text(size = 2, check_overlap = F, nudge_y = .2, data = cities, aes(x=long, y=lat, label = name)) +
    #theme(legend.key.size = unit(0.05, "cm")) + # legend.key.width=unit(1, "cm"), 
    ggmap::theme_nothing(legend = T) +
    theme(legend.title=element_text(size=5.5), legend.text=element_text(size=4)) +
    #theme(legend.position=c(0.075,0.28))
    guides(fill = guide_colorbar(barwidth = 0.5, barheight = 2.5)) +
    ggtitle(t)
  ggsave(p, filename = paste(path.out, t, ".png", sep = ""))
}

# geo_sf solution. same as lisa, but squeese hexagons
# gb %>% st_as_sf(crs = 27700) %>% 
# ggplot() + 
#     geom_sf(fill=NA, color = "black", size = 0.1, alpha = 0.8) + #geom_point(data = help.df, aes(x=X,y=Y))
#     stat_binhex(data = help.df, aes(x=X,y=Y),bins=150) + 
#     # geom_polygon(data = gb.df, aes(x=long, y = lat, group = group), #gb.df
#     #              fill=NA, color = "black", size = 0.1, alpha = 0.8)+
#     
#     #coord_equal() +
#     scale_fill_gradientn(colours=c('light gray','blue'),
#                          name='Frequency',na.value=NA) + #, trans = "log10") +
#     
#     labs(x=NULL, y=NULL) +
#     geom_point(data = cities, aes(x=long, y=lat), colour = "black", size = .1) + 
#     geom_text(size = 2, check_overlap = F, nudge_y = .2, data = cities, aes(x=long, y=lat, label = name)) +
#     #theme(legend.key.size = unit(0.05, "cm")) + # legend.key.width=unit(1, "cm"), 
#     ggmap::theme_nothing(legend = T) +
#     theme(legend.title=element_text(size=5.5), legend.text=element_text(size=4)) +
#     #theme(legend.position=c(0.075,0.28))
#     guides(fill = guide_colorbar(barwidth = 0.5, barheight = 2.5)) +
#     ggtitle(t)
```
## hex heatmaps log transformed

### 2023-03-20 src/level_lisa_la.Rmd
lisa per firm

library(tidyverse)
library(rprojroot)
library(rgdal)
library(rgeos)
library(spdep)
library(tmap)
library(maptools)
library(knitr)
library(REAT)
library(tidygeocoder)
library(geosphere)
library(broom)

@@

@@

path.out <- paste0(path, "/outputs/lisa_level_pc", n, "_la") # for unique PC
#path.out <- paste0(path, "/outputs/lisa_level_pc", m, "_la")  # for multiple PC

@@

@@

```{r}
path.out <- paste0(path, "/outputs/morani_la.csv")
morani %>% as_tibble() %>% 
  rename('morani'=V1,
                   p = V2,
                   year = V3) %>% 
  #kable() %>% 
  write_csv(path.out)

@@

path.out <- paste0(path,"/outputs/rsq_dist_london_la.png")
ggplot(dens.London) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to London on website density, LA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_london_la.png")
ggplot(out.model, aes(x=reorder(year, year), y=estimate)) +
#ggplot(out.model, aes(x=year, y = estimate)) +  
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to London on website density, LA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)
```

@@

path.out <- paste0(path,"/outputs/rsq_dist_city_la.png")
ggplot(dens.distMet) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to nearest city on website density, LA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_city_la.png")
ggplot(out.modelMet, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest city on website density, LA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)
```

@@

for (t in 1996:2012){
  model <- lm(log(density+0.001) ~ log(dist.retail+0.001), data = df[df$year==t,])
  r2 <- as.data.frame(summary(model)$r.squared)
  r2$year = t
  dens.dist.retail <- rbind(r2, dens.dist.retail)

@@

path.out <- paste0(path,"/outputs/rsq_dist_centre_la.png")
ggplot(dens.dist.retail) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to nearest retail centre on website density, LA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_centre_la.png")
ggplot(out.model.retail, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest city on website density, LA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

>>>>

library(tidyverse)
library(rprojroot)
library(rgdal)
library(rgeos)
library(spdep)
library(tmap)
library(maptools)
library(knitr)
library(REAT)
library(tidygeocoder)
library(geosphere)
library(broom)
library(foreach)
library(raster)

@@

## Firms

```{r}
firms <- read_csv("https://www.nomisweb.co.uk/api/v01/dataset/NM_142_1.data.csv?geography=1811939329...1811939332,1811939334...1811939336,1811939338...1811939428,1811939436...1811939442,1811939768,1811939769,1811939443...1811939497,1811939499...1811939501,1811939503,1811939505...1811939507,1811939509...1811939517,1811939519,1811939520,1811939524...1811939570,1811939575...1811939599,1811939601...1811939628,1811939630...1811939634,1811939636...1811939647,1811939649,1811939655...1811939664,1811939667...1811939680,1811939682,1811939683,1811939685,1811939687...1811939704,1811939707,1811939708,1811939710,1811939712...1811939717,1811939719,1811939720,1811939722...1811939730,1811939757...1811939767&date=latestMINUS10&industry=37748736&employment_sizeband=0&legal_status=0&measures=20100") %>% 
  select(GEOGRAPHY_CODE, OBS_VALUE) %>% #GEOGRAPHY_NAME, 
  rename(ladcd = GEOGRAPHY_CODE,
         firms = OBS_VALUE)

df <- df %>% left_join(firms) %>% 
  mutate(n_by_firm = n/firms) %>% # N websites/firm
  #filter(!is.na(firms)) %>% 
  select(-n, -firms) %>% 
  rename(n = n_by_firm)

# df %>% filter(is.na(n_by_firm))
# sapply(df %>% left_join(firms), function(x) sum(is.na(x)))
```

@@

path.out <- paste0(path, "/outputs/lisa/lisa_level_pc", n, "_la") # for unique PC
#path.out <- paste0(path, "/outputs/lisa/lisa_level_pc", m, "_la")  # for multiple PC

@@

## lisa maps parallel

path.out <- paste0(path, "/outputs/lisa/lisa_level_pc_test", n, "_la") # for unique PC
#path.out <- paste0(path, "/outputs/lisa/lisa_level_pc", m, "_la")  # for multiple PC

#setup cluster
#https://www.blasbenito.com/post/02_parallelizing_loops_with_r/
n.cores <- parallel::detectCores() - 1
my.cluster <- parallel::makeCluster(
  n.cores, 
  type = "PSOCK"
  )
print(my.cluster)
doParallel::registerDoParallel(cl = my.cluster)
foreach::getDoParWorkers()

#for (t in 1996:2012){
foreach(t = 1996:2012, .packages = c("tidyverse",
                                     "rgdal",
                                     "rgeos",
                                     "spdep",
                                     "tmap",
                                     "maptools",
                                     "knitr",
                                     "broom")) %dopar% {
test <- la
test@data <- test@data %>% left_join(df[df$year==t,], by = c("LAD21CD"="ladcd")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),           # 0 for NAs and the same for year
         year = ifelse(is.na(year), t, year))

map <- tm_shape(mun_merge_new, projection = "+init=epsg:4326") + tm_fill(col = "quadrant", breaks = breaks, 
                                         palette = c("white","red","blue",
                                                     rgb(0,0,1,alpha=0.4),
                                                     rgb(1,0,0,alpha=0.4)), 
                                         labels = c("Not significant", "High-High","Low-Low","Low-High","High-Low"), 
                                         title="LISA for level, LA") +
  tm_legend(text.size = 1) +
  #tm_scale_bar(position = c("LEFT", "BOTTOM"),text.size = 1.0)+
  #tm_compass(type = "8star",   position = c("RIGHT", "BOTTOM"),      show.labels = 2,   text.size = 0.5)+
  #tm_borders(alpha=.1) +
  tm_borders(lwd = 0) +
  tm_shape(la, simplify = .2) + tm_borders(alpha=1, lwd = .7) +
  tm_shape(tif_sf) + tm_dots() + tm_text("name", size = .5) +
  tm_layout( frame = FALSE,  title = t) #"LISA with the R p-values ") +
tmap_options(check.and.fix = TRUE)
tmap_save(map, filename = paste(path.out, t, ".png", sep = ""))
}

#ggplot map solution.
# mun_merge_new %>% st_as_sf(crs = 27700) %>% #st_transform(4326) %>%
#   ggplot()+
#   geom_sf(aes(fill = as.factor(quadrant)))
# ggsave("test_ggplot.png", path = path)
```

@@

```{r}
path.out <- paste0(path, "/outputs/lisa/morani_la.csv")
morani %>% as_tibble() %>% 
  rename('morani'=V1,
                   p = V2,
                   year = V3) %>% 
  #kable() %>% 
  write_csv(path.out)

@@

path.out <- paste0(path,"/outputs/rsq_dist_london_la.png")
ggplot(dens.London) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to London on website density, LA") +
  theme(plot.title = element_text(hjust = 0.5))
ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_london_la.png")
ggplot(out.model, aes(x=reorder(year, year), y=estimate)) +
#ggplot(out.model, aes(x=year, y = estimate)) +  
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to London on website density, LA") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)
```

@@

path.out <- paste0(path,"/outputs/rsq_dist_city_la.png")
ggplot(dens.distMet) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to nearest city on website density, LA") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_city_la.png")
ggplot(out.modelMet, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest city on website density, LA") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)
```

@@

for (t in 1996:2012){
  model <- lm(log(n+0.001) ~ log(dist.retail+0.001), data = df[df$year==t,]) #density
  r2 <- as.data.frame(summary(model)$r.squared)
  r2$year = t
  dens.dist.retail <- rbind(r2, dens.dist.retail)

@@

path.out <- paste0(path,"/outputs/rsq_dist_centre_la.png")
ggplot(dens.dist.retail) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to nearest retail centre on website density, LA") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_centre_la.png")
ggplot(out.model.retail, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest retail centre on website density, LA") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)
